External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-10-27 CVPR2017_Review_Unified.tex
add

\section{The Denoising Algorithm}
\subsection{Fast Patch Group Searching by Integral Image}

The searching of patch groups in images is inefficient if we search non-local similar patches to each local patch. To speed up the searching process and make our proposed method faster, we employ the technique of 'Summed Area Table' \cite{sat} for efficient PG searching. The SAT permits to evaluate the sum of pixel values in rectangular regions of the image with four operations, regardless of the region size. That is to say, we do not need do distance measure for each patch. It was first proposed under the name of summed area table\cite{viola2004robust}

\subsection{Prior Weights for Sparse Coding}
To remove the real noise, we employ the sparse coding framework. And in order to be adaptive to the input image, we employ the internal learned $\mathbf{U}$ of each cluster as an adaptive dictioanry to represent the structural variations of the PGs in that cluster. Since the $\mathbf{U}$ is orthonormal, its \emph{mutual incoherence} is naturally $0$ and therefore better than other redundant dictionaries.

>>>>

\section{The Denoising Algorithm}
\subsection{Fast Internal Patch Group Searching}

Given a RGB image of size $256\times256\times3$, we can extract over 60 thousands local patches of size $6\times6\times3$. It is time-consumming to search patch groups (PG) for local patches one by one. To speed up the searching process, we employ the technique of 'Summed Area Table' \cite{sat} for efficient PG searching. The SAT permits to evaluate the sum of pixel values in rectangular regions of the image with four operations, regardless of the region size. Hence, we do not need do distance measure for each local patch.

\subsection{Prior Weights for Sparse Coding}

To remove the real noise, we employ the sparse coding framework. And in order to be adaptive to the input image, we employ the internal learned $\mathbf{U}$ of each cluster as an adaptive dictioanry to represent the structural variations of the PGs in that cluster. Since the $\mathbf{U}$ is orthonormal, its \emph{mutual incoherence} is naturally $0$ and therefore better than other redundant dictionaries.
